---
title: "Data Publications - Science - Maritimes Region"
date: "`r Sys.Date()`"
author: Brian Bower 
output:
  rmdformats::robobook:
    self_contained: true
    thumbnails: true
    lightbox: true
    gallery: false
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# requires R package `rmdformats`
```

# Why Publish Data to the Open Government Platforms

- Open Government data publication has been a Directive within DFO since 2014.

- The Open Government platforms are intended to provide users with easy access to authoritative data sources.

- Making data open improves and promotes communication, collaboration, decision making, and general efficiency.

# Open Government Platforms

- Marine Spatial Data Infrastructure (MSDI): Only accessible to DFO employees.

- Federal Geospatial Platform (FGP): Only accessible to federal and provincial government employees.

- Open Government Portal: Open Data

# Typical Flexible Publication Process 

Minimum requirement for Open Data publication is general description of the data and GIS compatible datasets.

Your Maritimes Region Open Data technician (Brian Bower) and your Division Data Manager can help with the rest!

- Provide data and metadata to ODIS
- ODIS coordinates with teams to build GIS package
- ODIS Coordinates Publication with IMTS

# List of Publications


```{r echo=FALSE, include=FALSE, cache=FALSE}
library(readxl)
library(kableExtra)
library(dplyr)

eGIS <- read_excel('MaritimesFGP_InventoryBrianBower_All.xlsx', sheet = "eGIS") 

FGPdata <- read_excel('MaritimesFGP_InventoryBrianBower_All.xlsx', sheet = "FGP")
FGPdata <- dplyr::filter(FGPdata, !is.na(FGPdata$`FGP Records`))

```

## Internal eGIS Data
```{r }
kable(dplyr::select(eGIS, c("eGIS Publication Name", "REST URL", "eGIS URL")))
```

## FGP
```{r }
kable(dplyr::select(FGPdata, c("FGP Records", "Status", "Notes", "FGP URL", "Open Data URL", "Year" , "Fiscal Year Published")))
```







